Overview and Status of Assumptions of Physics\footnote{http://assumptionsofphysics.org} \\ \ifextended (Extended version) \else (Short version) \fi

### 2020-04-01 Articles/Overview/overview.tex
Adding comments

\extendedtrue

@@

@@

\textbf{Give science sturdier mathematical grounds.} There is a general sense within physics that, at some point, mathematical details are physically not interesting and should be handled ``appropriately'' by mathematicians. Therefore even mathematical structures that originally came from physics are now formalized by mathematicians to solve their own needs, and not the physicist's. This, in turns, reinforces the idea that those details are not interesting to the physicists. The reality is that a well-posed physical problem must also be a well-posed mathematical problem, but not the other way around, so leaving the details to the mathematicians means having fundamental structures that are less physical.\footnote{For example, quantum states are modeled with Hilbert spaces even though we know they contain mathematical objects that are unphysical.} Mathematicians will come up with definitions so that theorems are easier to prove or calculations are easier to perform. They will not come up with definitions based on whether they are physically meaningful. If we give a theory, as we said before, by simply stating a mathematical structure, then there is no guarantee that what we give is a fully physical theory. Unphysical elements simply means the physical problem was not specified correctly. If we truly are able to give a precise physical meaning to every mathematical object, then our formal structures will map one-to-one to our physical understanding. This means no unphysical mathematical artifacts and a more precise mathematical treatment of physics.

@@

\textbf{Physical theories.} This studies the different assumptions that are needed to recover the known physical theories. The assumptions typically describe what level of description is available for the system and its parts, how does it change in time and whether trajectories are enough to recover it.

@@

This part has not yet been formally developed, though some common ideas are starting to emerge. The main idea comes from the realization that, when defining a system, the notions of states, processes, time, evolution laws, interaction with the environment and equilibria are all interrelated and can't be given independently. Roughly speaking, to define a system we have to choose a boundary that separates it from the environment. Only the quantities that are unaffected by the interaction with the environment can, in those circumstances, be thought as properties of the system. This in turns is linked to what we can define as state for the system, which is linked to the laws we can write. The processes and the laws are naturally linked to what is assumed about time.

>>>>

\extendedfalse

@@

\ifextended (This extended version contains the same material of the short version, but adds more detail.)
\else (This short version contains the basic ideas and skips on the details.)
\fi

@@

\textbf{Give science sturdier mathematical grounds.} There is a general sense within physics that, at some point, mathematical details are physically not interesting and should be handled ``appropriately'' by mathematicians. Therefore even mathematical structures that originally came from physics are now formalized by mathematicians to solve their own needs, and not the physicist's. This, in turns, reinforces the idea that those details are not interesting to the physicists. The reality is that a well-posed physical problem must also be a well-posed mathematical problem, but not the other way around, so leaving the details to the mathematicians means having fundamental structures that are less physical.\footnote{For example, quantum states are modeled with Hilbert spaces even though we know they contain mathematical objects that are unphysical.} Mathematicians will come up with definitions so that theorems are easier to prove or calculations are easier to perform. They will not come up with definitions based on whether they are physically meaningful. If we give a theory, as we said before, by simply stating a mathematical structure, then there is no guarantee that what we give is a fully physical theory. Unphysical elements (e.g. mathematical solutions that do not correspond to a physical case) simply means the physical problem was not specified correctly. If we truly are able to give a precise physical meaning to every mathematical object, then our formal structures will map one-to-one to our physical understanding. This means no unphysical mathematical artifacts and a more precise mathematical treatment of physics.

@@

\textbf{Physical theories.} This studies the different assumptions that are needed to recover the known physical theories. The assumptions typically describe what level of description is available for the system and its parts, how does it change in time and whether trajectories are enough to recover all information.

@@

This part has not yet been formally developed, though some common ideas are starting to emerge. The main idea comes from the realization that, when defining a system, the notions of states, processes, time, law of evolution, interaction with the environment and equilibria are all interrelated and can't be given independently. Roughly speaking, to define a system we have to choose a boundary that separates it from the environment. Only the quantities that are unaffected by the interaction with the environment can, in those circumstances, be thought as properties of the system. This in turns is linked to what we can define as state for the system, which is linked to the laws we can write. The processes and the laws are naturally linked to what is assumed about time.
